\textbf{SPECFEM3D}\\ \textbf{Cartesian}\\ \textbf{User Manual}

### 2021-11-25 doc/USER_MANUAL/06_fault_sources.tex
Add read-from-file option for heterogeneous fault parameters (#2)
* Add read-from-file option for heterogeneous fault parameters

* Update user manual for read-from-file

* Minor edits of user manual

* Minor edits of user manual

* Minor edits in User_manual

* Minor edits in User_manual

* Minor edits in User_manual

* Minor edits in User_manual

* Minor edits in User_manual

* Minor edits in User_manual

\&\textbf{SWF} mus, mud, dc {[}, nmus, nmud, ndc{]} (weakening_kind=1 for linear (default); weakening_kind=2 for exponential)/

@@

\item [{\&\textbf{SWF}}] input block sets the slip-weakening friction parameters
of the fault:
\begin{description}
\item [{mus}] = constant background value of static friction coefficient
\item [{mud}] = constant background value of dynamic friction coefficient
\item [{dc}] = constant background value of critical slip-weakening distance
\item [{C}] = constant background value of cohesion (in Pa)
\item [{nmus}] = number of heterogeneous items for static friction coefficient
{[}default is 0{]}
\item [{nmud}] = number of heterogeneous items for dynamic friction coefficient
{[}default is 0{]}
\item [{ndc}] = number of heterogeneous items for critical slip-weakening
distance {[}default is 0{]}
\item [{nC}] = number of heterogeneous items for cohesion
\item [{weakening_kind}] = 1 for linear slip-weakening law (default); 2 for exponential slip-weakening law: $$\mu_d + (\mu_s-\mu_d) \exp(-\frac{u}{d_c})$$
\end{description}

@@

$\;$sets a constant value (val) within a sphere with center (xc,yc,zc)
and radius r. \\

>>>>

\&\textbf{SWF} mus, mud, dc {[}, nmus, nmud, ndc{]} (weakening\_kind=1 for linear (default); weakening\_kind=2 for exponential)/

@@

\item [{\&\textbf{SWF}}] input block sets the slip-weakening friction parameters
of the fault:
\begin{description}
\item [{mus}] = constant background value of static friction coefficient
\item [{mud}] = constant background value of dynamic friction coefficient
\item [{dc}] = constant background value of critical slip-weakening distance
\item [{C}] = constant background value of cohesion (in Pa)
\item [{nmus}] = number of heterogeneous items for static friction coefficient
{[}default is 0{]}
\item [{nmud}] = number of heterogeneous items for dynamic friction coefficient
{[}default is 0{]}
\item [{ndc}] = number of heterogeneous items for critical slip-weakening
distance {[}default is 0{]}
\item [{nC}] = number of heterogeneous items for cohesion
\item [{weakening\_kind}] = 1 for linear slip-weakening law (default); 2 for exponential slip-weakening law:
                            $$\mu = \mu_d + (\mu_s-\mu_d) exp(-\frac{u}{d_c}) $$
\end{description}

@@

$\;$sets a constant value (val) within a sphere with center (xc,yc,zc)
and radius r.

\&\textbf{DIST2D} shapeval='$\mathtt{read-from-file}$', filename
/

$\;$sets the name of the filename saved in the DATA directory. 
The first line in the file shall be the number of data points and the 
following lines in the file has the format: 
x, y, z, val. Method of interpolation is nearest. 
\\
